The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2014-07-03 article.tex
work on fingerprint table

% Load packages
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage{cite}

@@

%% Use of \listoftables is discouraged.
%%
%\section*{Tables}
%  \subsection*{Table 1 - Sample table title}
%    Here is an example of a \emph{small} table in \LaTeX\ using  
%    \verb|\tabular{...}|. This is where the description of the table 
%    should go. \par \mbox{}
%    \par
%    \mbox{
%      \begin{tabular}{|c|c|c|}
%        \hline \multicolumn{3}{|c|}{My Table}\\ \hline
%        A1 & B2  & C3 \\ \hline
%        A2 & ... & .. \\ \hline
%        A3 & ..  & .  \\ \hline
%      \end{tabular}
%      }
%  \subsection*{Table 2 - Sample table title}
%    Large tables are attached as separate files but should
%    still be described here.

>>>>

% Load packages
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
\usepackage{amssymb}
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage{cite}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
    \par
    \mbox{
    \begin{tabular}{lcclrc}
                             & Bit version  & Count version & CDK version & Default Size & References \\
  \cline{2-6}\noalign{\smallskip}
  EStateFingerprinter        & $\checkmark$ &               & 1.2.0       & $79$         & \cite{Hall1995}\\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         &              & \\
  Fingerprinter              & $\checkmark$ &               & 1.0         &              & \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         &              & \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       &              & \\
  KlekotaRothFingerprinter   & $\checkmark$ &               & 1.4.6       & $4\,860$     & \cite{Klekota2008}\\
  LingoFingerprinter         & $\checkmark$ &               & 1.6.0 ?     &              & \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       &              & \\
  PubchemFingerprinter       & $\checkmark$ &               & 1.4.0       &              & \\
  ShortestPathFingerprinter  & $\checkmark$ &               & 1.6.0 ?     &              & \\
  SignatureFingerprinter     & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $2^{32}$     & [pending] \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         &              & \\
    \end{tabular}}

%    Here is an example of a \emph{small} table in \LaTeX\ using  
%    \verb|\tabular{...}|. This is where the description of the table 
%    should go. \par \mbox{}
%    \par
%    \mbox{
%      \begin{tabular}{|c|c|c|}
%        \hline \multicolumn{3}{|c|}{My Table}\\ \hline
%        A1 & B2  & C3 \\ \hline
%        A2 & ... & .. \\ \hline
%        A3 & ..  & .  \\ \hline
%      \end{tabular}
%      }
%  \subsection*{Table 2 - Sample table title}
%    Large tables are attached as separate files but should
%    still be described here.
